Synpotic Soil Characterization

### 2025-07-28 3-reports/manuscript_figures.Rmd
add NH4N to figures

```{r v2-scaled_gg2_split-NEW, fig.height = 10, fig.width = 12}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

data_scaled_NEW2 = 
  data_scaled_NEW %>% 
  filter(name %in% c("WEOC", "TS", "Na", "Chloride", "Fe", "P")) %>% 
    mutate(name = factor(name, levels = c("TC", "TS", "WEOC",
                                        "Ca", "Na", "Chloride",
                                        "NH4N", "Fe", "P")))

>>>>

```{r v2-scaled_gg2_split-NEW, fig.height = 13, fig.width = 12}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

data_scaled_NEW2 = 
  data_scaled_NEW %>% 
  filter(name %in% c("WEOC", "TS", "Na", "Chloride", "Fe", "P", "NH4N")) %>% 
    mutate(name = factor(name, levels = c("TC", "TS", "WEOC",
                                        "Ca", "Na", "Chloride",
                                        "Fe", "P", "NH4N")))
